The Birth of a Galaxy: Primordial Metal Enrichment and Stellar Populations

### 2011-09-08 ApJ/ms.tex
Incorporated changes from Mike's comments and corrections.

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that follows the
  transition from Population III to II star formation.  We model
  stellar radiative feedback with adaptive ray tracing.  A top-heavy
  initial mass function for the Population III stars is considered,
  resulting in a plausible distribution of pair-instability supernovae
  and associated metal enrichment.  We find that the gas fraction
  recovers from 5 percent to nearly the cosmic fraction in halos with
  merger histories rich in halos above $10^7 \Ms$.  A single
  pair-instability supernova is sufficient to enrich the host halo to
  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
  Population II star formation.  This provides a natural explanation
  for the observed floor on damped Lyman alpha (DLA) systems
  metallicities reported in the literature, which is of this order.
  We find that stellar metallicities do not necessarily trace stellar
  ages, as mergers of halos with established stellar populations can
  create superpositions of $t-Z$ evolutionary tracks.  A bimodal
  metallicity distribution is created after a starburst occurs when
  the halo can cool efficiently through atomic line cooling.

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
stars enrich the surrounding intergalactic medium (IGM) when they go
supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.  The host
halo and the neighboring halos are then enriched with this ejecta.
There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
be occur if the gas cooling is suppressed to the cosmic microwave
background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
  2009ApJ...691..441S}.  The resulting Population II star cluster will
thus have a lower characteristic stellar mass than its metal-free
progenitors.  These first stellar clusters may be connected to stars
in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
both with a metallicity floor of [Z/H]\footnote{We use the
  conventional notation, [Z/H] $\equiv$ log(Z/H) -
  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
  Tafelmeyer10}.

@@

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  Here, we
present a simulation that includes both types of SF, and their
radiative and mechanical feedback.  The methods used here incorporate
and link together recent results from metal-enriched and metal-free
star formation, the critical metallicity, and pair-instability
supernovae.  This is the first time it has been possible to link the
formation and feedback of the first stars to protogalaxies, resolving
the important scales and including the most important physical
effects.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a}.  They
form in molecular clouds that coexist with the dark matter halo center
with limited fragmentation occurring during their collapse; however
\citet{2009Sci...325..601T} and \citet{Stacy10_Binary} have recently
shown that Pop III binaries may form in a fraction of such halos.

@@

For Pop III stars, we use the same SF model as \citet{Wise08_Gal}
where each star particle represents a single star, forming at an
overdensity of $5 \times 10^5$ ($\sim 10^3\; \cubecm$ at $z=10$).  If
multiple cells meet the star particle formation criteria within 1 pc,
we form one Pop III star particle with the center of mass of these
flagged cells to ensure that massive star is created per metal-free
molecular cloud.  Instead of using a fixed stellar mass like in our
previous work, we randomly sample from an IMF with a functional form
of
%
\begin{equation}
\label{eqn:imf}
f(\log M) dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
      char}}{M}\right)^{1.6}\right] dM
\end{equation}
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we record the number
of times the random number generator (Mersenne twister;
\citet{MTwister}) has been called for use when restarting the
simulations.

@@

We treat Pop II star formation with the same prescription as
\citet{Wise09}, which is similar to the Pop III prescription but
without the \hh~fraction floor that is removed because the
metal-enriched gas can efficiently cool even in the presence of a
strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
effectively a modified version of the \citet{Cen92} method but
accounts for the fact that the molecular clouds are resolved.  In the
simulation, we define the molecular cloud as a sphere, centered on the
most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
R_{\rm MC}^3$.  We then replace the sphere with a uniform density
$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
= 10^4$ K, which approximates the initial stages of an \ion{H}{2}
region.  Similar to the Pop III treatment, we merge any newly created
particles within a radius of 10 pc.  We set the minimum mass of a star
particle to $m_{\rm \star, min} = 1000 \Ms$.  If the initial mass does
not exceed $m_{\rm \star, min}$, the star particle does not provide
any feedback and continues to accrete until it reaches $m_{\rm \star,
  min}$.  The star particles live for 20 Myr, the maximum lifetime of
an OB star.  These stars generate the majority of the ionizing
radiation and SNe feedback in stellar clusters, thus we ignore any
feedback from lower mass stars.

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise11_Moray} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
Each star particle is a point source of hydrogen ionizing radiation
with the ionizing luminosity equally split between 48 initial rays
(HEALPix level 2).  We use a mono-chromatic spectrum for the radiation
with the energy $E_{\rm ph}$ equaling the luminosity-weighted photon
energy of the spectrum.  For a cosmological simulation that focuses on
galaxies, this does not significantly affect the overall galactic
dynamics \citep[see Sec. 6.3 in][]{Wise11_Moray}.  We do not consider helium
singly- and doubly-ionizing radiation.  As the rays propagate from the
source or into a high resolution AMR grid, they are adaptively split
into 4 child rays, increasing the angular resolution of the solution,
when the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is
larger than 1/3 of the cell area, where $L$ is the HEALPix level.  We
model the \hh~dissociating radiation with an optically-thin, inverse
square profile, centered on all star particles.  In haloes with $M
\ga 10^8 \Ms$, the \hh~column density may become large enough to
self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we may
be underestimating the SFRs in our work.

We use mass-dependent hydrogen ionizing and LW photon luminosites and
lifetimes of the Pop III stars from \citet{Schaerer02}.  We use a
mass-independent photon energy $E_{\rm ph} = 29.6$ eV, appropriate for
the near-constant $10^5$ K surface temperatures of Pop III stars.
They die as Type II SNe if $11 \le M_\star/\Ms \le 40$
\Ms~\citep{Woosley95} and as PISNe if they are in the mass range
140--260 \Ms~\citep{Heger03}, where $M_\star$ is the stellar mass.
For normal Type II SNe between 11--20 \Ms, we use an explosion energy
of \tento{51}~erg and a linear fit to the metal ejecta mass calculated
in \citet{Nomoto06},
%
\begin{equation}
  \label{eqn:typeii}
  M_{\rm Z}/\Ms = 0.1077 + 0.3383 \times (M_\star/\Ms - 11).
\end{equation}
%
We model the SNe of stars with $20 \le M_\star/\Ms \le 40$ as
hypernova with the energies and ejecta masses also taken from
\citeauthor{Nomoto06}, linearly interpolating their results to
$M_\star$.  For PISNe, we use the explosion energy from
\citet{Heger02}, where we fit the following function to their models,
%
\begin{equation}
  \label{eqn:pisn}
  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \; \mathrm{erg},
\end{equation}
%
where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium
core (and equivalently the metal ejecta) mass and $M_\star$ is the
stellar mass.  The blastwave is modeled by injecting the explosion
energy and ejecta mass into a sphere of 10 pc, smoothed at its surface
to improve numerical stability \citep{Wise08_Gal}.  Because we resolve
the blastwave relatively well with several cells across at its
initialization, the thermal energy is converted into kinetic energy
and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.

@@

\begin{figure}
\epsscale{1.15}
\plotone{f2}
\epsscale{1}
  \caption{\label{fig:halo-mosaic} Density-weighted projections of
    density (left), temperature (center), and metallicity (right) of
    the two selected haloes at $z=7$.  The field of view is 5 proper
    kpc, and the circles have a radius of $r_{200}$.  The composite
    metallicity images are constructed in the same fashion as
    Fig. \ref{fig:evo-mosaic}.}
\end{figure}

@@

\begin{figure}
\epsscale{1.15}
\plotone{f3}
\epsscale{1}
\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
  (solid) and III (dashed).  Note that the Pop III rates are nearly
  constant from redshift 12 to 7.  Pristine haloes still survive in
  underdense regions, supporting late-time metal-free star formation.}
\end{figure}

@@

We illustrate the evolution of the simulation from $z=15$ to $z=7$ in
Figure \ref{fig:evo-mosaic} with density weighted projections of gas
density, temperature, and metallicity of the entire box.  Figure
\ref{fig:halo-mosaic} shows the same types of plots but focusing on
the two halos of interest with a field of view of 5 proper kpc.
Radiative and mechanical feedback create a multi-phase medium inside
these halos, which are embedded in a warm and ionized IGM.  At the
final redshift, the volume and mass ionized fraction are 0.76 and
0.72, respectively, which are consistent with large-scale reionization
simulations \citep{Zahn11}.  PISNe enrich 0.106 and 0.027 of the mass
and volume, respectively, above $10^{-3} \zsun$, and 0.034 and 0.0024
of the mass and volume are enriched by Type II SNe above the same
threshold.  Table \ref{tab:enrich} gives additional enriched fractions
with different metallicity cuts.

@@

Figure \ref{fig:sfr} shows the cosmic SFR in the simulation for Pop II
and III stars.  Metal-free stars form at a nearly constant rate of $5
\times 10^{-4}$ \sfr~until the end of the simulation.  The
dissociating and ionization radiation from nearby Pop III stars and
galaxies do not halt the formation of such stars in low-mass haloes
but only suppress them.  We expect a uniform \hh~dissociating
radiation background to further delay them \citep{Machacek01, Wise07,
  OShea08}.

@@

To further demonstrate the metallicity floor in high-redshift dwarf
galaxies, we show the average metallicity from Pop III SNe \zthree~in
all haloes as a function of halo mass at $z =$ 7, 8, 9, and 10 in
Fig. \ref{fig:z3}, and it is strongly dependent on halo mass.  The
\zthree~error bars mark the 25\% and 75\% percentiles of the
distribution at $M = M_{\rm halo}$ because the underlying distribution
is not necessarily Gaussian at all halo masses.  Above $3 \times 10^7
\Ms$, all haloes enriched to $\zthree \ga -4$ with little time
evolution, further illustrating the metallicity floor.  Below this
halo mass, the distribution is roughly bimodal composed of pristine
and metal-enriched halos.

@@

The most massive progenitor of the quiet halo interestingly never
hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
the most massive progenitor, and the dense core survives this event
and is enriched by this PISN, triggering the transition to Pop II SF.
Other progenitors host three Pop III stars, forming at $z = 15.4,
14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
these two PISNe and Pop II SF quench Pop III SF in this halo.  The
progenitors of the intense halo host a total of 56 Pop III stars with
21 producing PISNe.  The first forms in a $6 \times 10^5 \Ms$ halo at
$z=19$.  Pop III stars form on a regular interval in the halo's
progenitors until $z=9$ when most of these halos enter the metal-rich
bubble surrounding the intense halo.

@@

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM
  \nonumber\\ &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because the total luminosity of
low-mass stars is negligible.  Then the galaxy luminosity is the sum
of all star particle luminosities, which we plot in
Fig. \ref{fig:massfn} with respect to halo mass, along with the DM
halo mass function.

@@

We have focused on the birth of two galaxies prior to reionization
with a cosmological AMR radiation hydrodynamics simulation.
Supernovae from Pop III stars provide the necessary heavy elements for
the transition to a Population II stellar population, which we have
directly simulated.  These two galaxies have a 10--15\% probability in
surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
otherwise they will be incorporated into galactic stellar halos.  A
$z=8.55$ galaxy was recently spectroscopically confirmed that is
contained in an ionized bubble with radius 0.1--0.5 Mpc with an
uncharacterized population of galaxies contributing to the local
ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
simulated here might represent this population and should be detected
with the upcoming \textit{James Webb Space Telescope}.

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review}, and metal enrichment from Pop
III SNe provides a possible explanation \citep{Kobayashi11}.

>>>>

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3.5}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that follows the
  transition from Population III to II star formation.  The maximum
  spatial resolution of 1 comoving parsec is an order of magnitude
  improvement over previous dwarf galaxy simulations, allowing for
  individual molecular clouds to be well-resolved and their stellar
  associations to be studied in detail.  We model stellar radiative
  feedback with adaptive ray tracing.  A top-heavy initial mass
  function for the Population III stars is considered, resulting in a
  plausible distribution of pair-instability supernovae and associated
  metal enrichment.  We find that the gas fraction recovers from 5
  percent to nearly the cosmic fraction in halos with merger histories
  rich in halos above $10^7 \Ms$.  A single pair-instability supernova
  is sufficient to enrich the host halo to a metallicity floor of
  $10^{-3} Z_\odot$ and to transition to Population II star formation.
  This provides a natural explanation for the observed floor on damped
  Lyman alpha (DLA) systems metallicities reported in the literature,
  which is of this order.  We find that stellar metallicities do not
  necessarily trace stellar ages, as mergers of halos with established
  stellar populations can create superpositions of $t-Z$ evolutionary
  tracks.  A bimodal metallicity distribution is created after a
  starburst occurs when the halo can cool efficiently through atomic
  line cooling.

@@

The first (Pop III) stars are metal-free and have a large
characteristic mass and suppressed fragmentation in its protostellar
collapse \citep{ABN02, Bromm02_P3, OShea07a}.  A fraction of these
stars enrich the surrounding intergalactic medium (IGM) when they go
supernova, which can happen in stars $\lsim 40~\Ms$ in Type II
supernovae (SNe) or in stars roughly between 140 \Ms~and 260 \Ms~in
pair-instability SNe \citep[PISNe;][]{2002ApJ...567..532H}.  The host
halo and the neighboring halos are then enriched with this ejecta.
There exists a critical metallicity that is $\sim 10^{-6} Z_\odot$ if
dust cooling is efficient \citep{Omukai05, Schneider06_Frag, clark08}
and $\sim 10^{-3.5} Z_\odot$ otherwise \citep{Bromm01,
  2009ApJ...691..441S}, where the gas can cool rapidly, lowering its
Jeans mass.  An intermediate characteristic mass of $\sim10~\Ms$ can
occur if the gas cooling is suppressed to the cosmic microwave
background (CMB) temperature \citep{Larson98, Tumlinson07_IMF,
  2009ApJ...691..441S}.  The resulting Population II star cluster will
thus have a lower characteristic stellar mass than its metal-free
progenitors.  These first stellar clusters may be connected to stars
in the Milky Way halo and nearby dwarf spheroidal (dSph) galaxies,
both with a metallicity floor of [Z/H]\footnote{We use the
  conventional notation, [Z/H] $\equiv$ log(Z/H) -
  log(Z$_\odot$/H$_\odot$).} = --4 \citep{Beers05, Frebel10_Obs,
  Tafelmeyer10}.

@@

Over the past decade, these works have refined the general picture of
inhomogenous metal enrichment and the transition to Pop II star
formation, and here we give an overview of its development.
Considering only Pop III star formation, \citeauthor{Yoshida04}
calculated that Pop III stars can raise the mean metallicity to $-4.5
\lsim$ [Z/H] $\lsim -3.5$ by redshift 15 in the upper limit where all
metal-free stars have $M = 200 \Ms$ and produce PISNe.  Considering
both Pop III and II star formation, \citeauthor{Scannapieco03} found
that the transition between the two modes is a gradual process where
both modes are coeval, confirmed by most of the later works.  Because
the host galaxies have small masses and are subject to negative
radiative feedback through photo-heating and photo-dissociation, the
minimum halo mass gradually increases with the radiation background
intensity, which \citeauthor{Furlanetto05_Reion} found to delay metal
enrichment and place it closer to the epoch of reionization.
\citeauthor{Trenti09} noted that underdense regions of the universe
are still pristine at $z=6$ with Pop III stars still forming at these
late epochs.  This group later expanded on these results to find that
Pop II SFR becomes dominant at $z>25$ in the buildup of a Milky Way
(MW) like halo.  Furthermore they stress the importance of a
photo-dissociating radiation background that reduces enrichment by
PISNe and increases the importance of metal-rich galactic outflows,
where only $10^{-4} - 10^{-2}$ of PISN ejecta ends up in extremely
metal poor (EMP) stars with $M > 0.9 \Ms$.

The Pop III IMF should play an important role in abundance patterns in
EMP stars in the MW halo and the physics of reionization.  Using these
data as constraints, \citeauthor{Tumlinson06} found that Pop III IMFs
with log-normal distributions with mean masses between 8 and 42
\Ms~best fit the data.  Furthermore he concludes that EMP stars with
[Z/H] $<$ --3 have between 1 and 10 metal-free SN progenitors and
the Pop III SFR is less than 1\% of the total SFR at $z=6$.
\citeauthor{Karlsson08} use observational data of EMP stars with
their model to constrain the mass fraction of Pop III stars that
die with a PISN is less than 40 per cent.  They also conclude that
stars enriched primarily by PISNe have [Ca/H] $\gsim$ --2.6, which
could have been missed by some EMP surveys.

These works have clearly shown that many processes play a key role in
the transition from Pop III to II stars, but how does their interplay
affect the formation of the first galaxies?  Will metal-free pockets
of gas still exist in dwarf galaxies that are already forming
metal-enriched stars?  How do the metal-enriched ejecta propagate into
future sites of star formation?  Numerical simulations are powerful
tools to detangle and study these complexities.  To answer such
questions, we have carried out a simulation that includes both types
of SF, and their radiative and mechanical feedback.  The methods used
here incorporate and link together recent results from metal-enriched
and metal-free star formation, the critical metallicity, and
pair-instability supernovae.  This is the first time it has been
possible to correlate the formation and feedback of the first stars to
protogalaxies, resolving individual molecular clouds and minihalos
down to $10^5 \Ms$ and including the most important physical effects,
such as radiative and supernova feedback.

@@

Simulations have shown that the characteristic mass of Pop III stars
$M_{\rm char} \sim 100~\Ms$ \citep{ABN02, Bromm02_P3, OShea07a,
  Yoshida08}.  They form in molecular clouds that coexist with the
dark matter halo center with limited fragmentation occurring during
their collapse; however \citet{2009Sci...325..601T} and
\citet{Stacy10_Binary} have recently shown that Pop III binaries may
form in a fraction of such halos.

@@

For Pop III stars, we use the same SF model as \citet{Wise08_Gal}
where each star particle represents a single star, forming at an
overdensity of $5 \times 10^5$ ($\sim 10^3\; \cubecm$ at $z=10$).  If
multiple cells meet the star particle formation criteria within 1 pc,
we form one Pop III star particle with the center of mass of these
flagged cells to ensure that massive star is created per metal-free
molecular cloud.  Instead of using a fixed stellar mass like in our
previous work, we randomly sample from an IMF with a functional form
of
%
\begin{equation}
\label{eqn:imf}
f(\log M) dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm
      char}}{M}\right)^{1.6}\right] dM
\end{equation}
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we record the
number of times the random number generator (Mersenne twister;
\citet{MTwister}) has been called for use when restarting the
simulations.  The Pop III IMF is highly uncertain.  In
Sec. \ref{sec:discuss}, we discuss possible dependencies of our
results to changes in the IMF.

@@

We treat Pop II star formation with the same prescription as
\citet{Wise09}, which is similar to the Pop III prescription but
without the \hh~fraction floor that is removed because the
metal-enriched gas can efficiently cool even in the presence of a
strong UV radiation field \citep[e.g.][]{Safranek10}.  This method is
effectively a modified version of the \citet{Cen92} method but
accounts for the fact that the molecular clouds are resolved.  In the
simulation, we define the molecular cloud as a sphere, centered on the
most dense cell, with a dynamical time $t_{\rm dyn} = 3$ Myr
(corresponding to an average density $\bar{\rho}_{\rm MC} \simeq
1000\mu \cubecm$) and a radius $R_{\rm MC}$, where $\mu$ is the mean
molecular weight.  In this sphere, a fraction $c_\star = 0.07 f_{\rm
  cold}$ of the cold gas ($T < 10^3$ K) is converted into a star
particle with mass $m_\star = c_\star (4\pi/3) \bar{\rho}_{\rm MC}
R_{\rm MC}^3$.  We then replace the sphere with a uniform density
$\rho_{\rm MC} = (1 - c_\star) / (Gt_{\rm dyn}^2)$ and temperature $T
= 10^4$ K, which approximates the initial stages of an \ion{H}{2}
region.  Similar to the Pop III treatment, we merge any newly created
particles within a radius of 10 pc.  We set the minimum mass of a star
particle to $m_{\rm \star, min} = 1000 \Ms$.  Unlike Pop III star
particles that represent individual stars, Pop II star particles
represent a star cluster of some total mass and an assumed normal IMF.
If the initial mass does not exceed $m_{\rm \star, min}$, the star
particle does not provide any feedback and continues to accrete until
it reaches $m_{\rm \star, min}$.  The star particles live for 20 Myr,
the maximum lifetime of an OB star.  These stars generate the majority
of the ionizing radiation and SNe feedback in stellar clusters, thus
we ignore any feedback from lower mass stars.

@@

The radiation field is evolved with adaptive ray tracing
\citep{Abel02_RT, Wise11_Moray} that is based on the HEALPix framework
\citep{HEALPix} and is coupled self-consistently to the hydrodynamics.
In this work, we only consider energy coupling to the gas; we defer an
investigation of the effects of radiation momentum coupling to a
subsequent paper.  Each star particle is a point source of hydrogen
ionizing radiation with the ionizing luminosity equally split between
48 initial rays (HEALPix level 2).  We use a mono-chromatic spectrum
for the radiation with the energy $E_{\rm ph}$ equaling the
luminosity-weighted photon energy of the spectrum.  For a cosmological
simulation that focuses on galaxies, this does not significantly
affect the overall galactic dynamics \citep[see Sec. 6.3
  in][]{Wise11_Moray}.  We do not consider helium singly- and
doubly-ionizing radiation.  As the rays propagate from the source or
into a high resolution AMR grid, they are adaptively split into 4
child rays, increasing the angular resolution of the solution, when
the solid angle of the ray $\theta = 4\pi/(12 \times 4^{L})$ is larger
than 1/3 of the cell area, where $L$ is the HEALPix level.  We model
the \hh~dissociating radiation with an optically-thin, inverse square
profile, centered on all Pop II and III star particles.  In halos
with $M \ga 10^8 \Ms$, the \hh~column density may become large enough
to self-shield itself from LW radiation \citep{Wise08_Gal}.  Thus we
may be underestimating the SFRs in our work.

We use mass-dependent hydrogen ionizing and LW photon luminosites and
lifetimes of the Pop III stars from \citet{Schaerer02}.  We use a
mass-independent photon energy $E_{\rm ph} = 29.6$ eV, appropriate for
the near-constant $10^5$ K surface temperatures of Pop III stars.
They die as Type II SNe if $11 \le M_\star/\Ms \le 40$
\Ms~\citep{Woosley95} and as PISNe if they are in the mass range
140--260 \Ms~\citep{Heger03}, where $M_\star$ is the stellar mass.
For normal Type II SNe between 11--20 \Ms, we use an explosion energy
of \tento{51}~erg and a linear fit to the metal ejecta mass calculated
in \citet{Nomoto06},
%
\begin{equation}
  \label{eqn:typeii}
  M_{\rm Z}/\Ms = 0.1077 + 0.3383 \times (M_\star/\Ms - 11).
\end{equation}
%
We model the SNe of stars with $20 \le M_\star/\Ms \le 40$ as
hypernova with the energies and ejecta masses also taken from
\citeauthor{Nomoto06}, linearly interpolating their results to
$M_\star$.  For PISNe, we use the explosion energy from
\citet{Heger02}, where we fit the following function to their models,
%
\begin{equation}
  \label{eqn:pisn}
  E_{\rm PISN} = 10^{51} \times [5.0 + 1.304 (M_{\rm He}/\Ms - 64)] \; \mathrm{erg},
\end{equation}
%
where $M_{\rm He} = (13/24) \times (M_\star - 20) \Ms$ is the helium
core (and equivalently the metal ejecta) mass and $M_\star$ is the
stellar mass.  If the stellar mass is outside of these ranges, then an
inert, collisionless black hole (BH) particle is created.

The blastwave is modeled by injecting the explosion energy and ejecta
mass into a sphere of 10 pc, smoothed at its surface to improve
numerical stability \citep{Wise08_Gal}.  Because we resolve the
blastwave relatively well with several cells across at its
initialization, the thermal energy is converted into kinetic energy
and agrees with the Sedov-Taylor solution \citep[e.g.][]{Greif07}.

@@

\begin{figure}
\epsscale{1.15}
\plotone{f2}
\epsscale{1}
  \caption{\label{fig:halo-mosaic} Density-weighted projections of
    density (left), temperature (center), and metallicity (right) of
    the two selected halos at $z=7$.  The field of view is 5 proper
    kpc, and the circles have a radius of $r_{200}$.  The composite
    metallicity images are constructed in the same fashion as
    Fig. \ref{fig:evo-mosaic}.}
\end{figure}

@@

\begin{figure}
\epsscale{1.15}
\plotone{f3}
\epsscale{1}
\caption{\label{fig:sfr} Cosmic star formation rates for Pop II
  (solid) and III (dashed).  Note that the Pop III rates are nearly
  constant from redshift 12 to 7.  Pristine halos still survive in
  underdense regions, supporting late-time metal-free star formation.}
\end{figure}

@@

We illustrate the evolution of the simulation from $z=15$ to $z=7$ in
Figure \ref{fig:evo-mosaic} with density weighted projections of gas
density, temperature, and metallicity of the entire box.  Figure
\ref{fig:halo-mosaic} shows the same types of plots but focusing on
the two halos of interest with a field of view of 5 proper kpc.
Radiative and mechanical feedback create a multi-phase medium inside
these halos, which are embedded in a warm and ionized IGM.  At the
final redshift, the volume and mass ionized fraction are 0.76 and
0.72, respectively, which are consistent with large-scale reionization
simulations \citep{Zahn11}.  PISNe enrich 0.065 and 0.019 of the mass
and volume, respectively, above $10^{-3} \zsun$, and 0.025 and 0.0010
of the mass and volume are enriched by Type II SNe from Pop II stars
above the same threshold.  With $M_{\rm char} = 100 \Ms$, a negligible
fraction of Pop III stars die as Type II SNe; thus, all metals
originating from Pop III stars are produced in PISNe.  Table
\ref{tab:enrich} gives additional enriched fractions with different
metallicity cuts.

@@

Figure \ref{fig:sfr} shows the cosmic SFR in the simulation for Pop II
and III stars.  Metal-free stars form at a nearly constant rate of $5
\times 10^{-5}$ \sfr~until the end of the simulation.  The
dissociating and ionization radiation from nearby Pop III stars and
galaxies do not halt the formation of such stars in low-mass halos
but only suppress them.  We expect a uniform \hh~dissociating
radiation background to further delay them \citep{Machacek01, Wise07,
  OShea08}.

@@

To further demonstrate the metallicity floor in high-redshift dwarf
galaxies, we show the average metallicity from Pop III SNe \zthree~in
all halos as a function of halo mass at $z =$ 7, 8, 9, and 10 in
Fig. \ref{fig:z3}, and it is strongly dependent on halo mass.  The
\zthree~error bars mark the 25\% and 75\% percentiles of the
distribution at $M = M_{\rm halo}$ because the underlying distribution
is not necessarily Gaussian at all halo masses.  Above $3 \times 10^7
\Ms$, all halos enriched to $\zthree \ga -4$ with little time
evolution, further illustrating the metallicity floor.  Below this
halo mass, the distribution is roughly bimodal composed of pristine
and metal-enriched halos.

@@

The most massive progenitor of the quiet halo interestingly never
hosts a Pop III star.  Instead a nearby halo forms a Pop III star,
which (randomly) produces a PISNe at $z=16$.  The blastwave overruns
the most massive progenitor, and the dense core survives this event
and is enriched by this PISN, triggering the transition to Pop II SF.
Other progenitors host three Pop III stars, forming at $z = 15.4,
14.2, 13.8$, with the latter producing a PISN.  Metal enrichment from
these two PISNe and Pop II SF quench Pop III SF in this halo.  The
progenitors of the intense halo host a total of 56 Pop III stars with
21 producing PISNe and the other 35 producing intermediate-mass BHs.
The first forms in a $6 \times 10^5 \Ms$ halo at $z=19$.  Pop III
stars form on a regular interval in the halo's progenitors until $z=9$
when most of these halos enter the metal-rich bubble surrounding the
intense halo.

@@

Mass-to-light ratios are crucial in interpreting observations when
connecting the galaxy to its DM halo, and ultimately to models of
galaxy formation.  For this paper, we use a simple model to calculate
the total stellar luminosity of each galaxy.  In a later paper, we
will follow up with more sophisicated models to determine more
accurate observables.  Stars in each particle are treated as an
instantaneous burst.  Using the empirical law of main sequence
lifetime $t_{\rm MS} \propto M^{-5/2}$, the maximum stellar mass in
such a system is dependent only on its age $t_\star$, so $M_{\rm up} =
(t_\star / 10\;\mathrm{Gyr})^{-2/5}$.  Then combining another scaling
law $L \propto M^{7/2}$ and the Salpeter IMF $\psi(M) \propto
M^{-\alpha}$,
%
\begin{eqnarray}
  \label{eqn:lum}
  L/M_\odot &=& \int_{M_{\rm lo}}^{M_{\rm up}} \psi(M) L(M) dM
  \nonumber\\ &\simeq& M_{\rm up}^{9/2-\alpha} (9/2 - \alpha)^{-1},
\end{eqnarray}
where we set $M_{\rm lo} \equiv 0$ because the total luminosity of
low-mass stars is negligible.  Then the galaxy luminosity is the sum
of all star particle luminosities, which we plot in
Fig. \ref{fig:massfn} with respect to halo mass, along with the DM
halo mass function.

@@

We have focused on the birth of two galaxies prior to reionization
with a cosmological AMR radiation hydrodynamics simulation with
unprecedented spatial (1 pc comoving) and mass resolution (1800 \Ms).
With this resolution, we are able to follow the Pop III star formation
and radiative and chemical feedback effects in hundreds of minihalos
that contribute to the formation of a protogalaxy.  Supernovae from
Pop III stars provide the necessary heavy elements for the transition
to a Population II stellar population, which we have directly
simulated.  These two galaxies have a 10--15\% probability in
surviving as present-day ``fossil'' galaxies \citep{Gnedin06},
otherwise they will be incorporated into galactic stellar halos.  A
$z=8.55$ galaxy was recently spectroscopically confirmed that is
contained in an ionized bubble with radius 0.1--0.5 Mpc with an
uncharacterized population of galaxies contributing to the local
ionizing radiation field \citep{Lehnert10_z8.6}.  The galaxies
simulated here might represent this population and should be detected
with the upcoming \textit{James Webb Space Telescope}.

We find that one PISN is sufficient to enrich the star-forming halo
and surrounding $\sim 5$ kpc to a metallicity of 10$^{-3} Z_\odot$,
given $M_{\rm char} = 100~\Ms$.  DLA systems have a metallicity floor
on the same order \citep{Wolfe05_Review, Penprase10}, and metal
enrichment from Pop III SNe provides a possible explanation
\citep{Kobayashi11}.  Ours is the first simulation with sufficient
physics and resolution to support this claim.
